\section{Problem Set 5}
\begin{problem}
    Let $a_n,b_n$ be two sequence of real numbers and $x$ be a real number. The fourier series is 
    \[ \frac{a_0}{2}+\sum_{n=1}^{\infty} a_n \cos(nx)+b_n \sin(nx) \]
    Show that if $\displaystyle \sum_{n=1}^{\infty} \left(|a_n|+|b_n|\right)$ converges, then so does the fourier series.
\end{problem}

\textit{Solution.}

We can ignore the $\dps \frac{a_0}{2}$ term and just focus on the sum. Let 
\[ S_N(x) = \sum_{n=1}^{N} a_n \cos(nx) + b_n \sin(nx) \]

We will show that the sequence $\{S_N(x)\}$ is cauchy. Let $N,M \in \NN$ such that $M>N$.
\[ |S_M(x)-S_N(x)| = \sum_{n=N+1}^{M} a_n \cos(nx) + b_n \sin(nx) \le \sum_{n=N+1}^{M} |a_n| + |b_n| \]
As $N \to \infty$ the $\dps \sum_{n=N+1}^{M} |a_n| + |b_n| \to 0$. Thus the sequence is cauchy and from the 
$\textbf{cauchy convergence theorem}$ we know the series converges.

\begin{problem}
    Give an example of a function $f(x)$ defined on $[-1,1]$ with the following property:
    $(f(x))^2$ is continuous on $[-1,1]$ but $f(x)$ is not continuous on $[-1,1]$.
\end{problem}

\textit{Solution.} 

An example of such a function would be 
\[ f(x) = \begin{cases}
    1 & \text{if } x > 0 \\
    -1 & \text{if } x \le 0 
\end{cases} \]

\begin{problem}
    Determine at which points the function $f(x)=\floor{x}$ is continuous or discontinuous.
\end{problem}

\textit{Solution.}

Let $n \in \mathbb{Z}$. Suppose, for contradiction, that $\lfloor x \rfloor$ is continuous at $x = n$. Then, by definition, for every $\varepsilon > 0$ there exists $\delta > 0$ such that
\[
|x - n| < \delta \implies |\lfloor x \rfloor - \lfloor n \rfloor| < \varepsilon.
\]

Take $\varepsilon = \frac{1}{2}$. Consider $x = n - \frac{\delta}{2}$. Clearly, $|x - n| = \frac{\delta}{2} < \delta$, so it should satisfy the continuity condition.  

However,
\[
\lfloor x \rfloor = \lfloor n - \tfrac{\delta}{2} \rfloor = n-1
\]
and
\[
\lfloor n \rfloor = n.
\]

Thus,
\[
|\lfloor x \rfloor - \lfloor n \rfloor| = |(n-1) - n| = 1 > \varepsilon = \frac{1}{2},
\]
which is a contradiction. Hence, $\lfloor x \rfloor$ is \textbf{discontinuous at every integer}.

\bigskip

Let $x_0 \notin \mathbb{Z}$ and set $n = \lfloor x_0 \rfloor$. Then $n < x_0 < n+1$. Define
\[
\delta = \min\{x_0 - n,\, n+1 - x_0\} > 0.
\]

For any $x$ with $|x - x_0| < \delta$, we have
\[
n < x < n+1 \implies \lfloor x \rfloor = n = \lfloor x_0 \rfloor.
\]

Hence,
\[
|\lfloor x \rfloor - \lfloor x_0 \rfloor| = 0,
\]
proving that $\lfloor x \rfloor$ is \textbf{continuous at every non-integer}.




