\begin{problem}
    A complex number $z$ is said to be algebraic if there exists integers $a_0,\ldots ,a_n$ not all zero such that
    \[ a_0 z^n + a_1 z^{n-1} + \cdots + a_{n-1} z + a_n = 0  \]  
    Prove that all the algebraic numbers are countable.
\end{problem}

\vspace{4mm}
\textit{Solution.}

For a given positive integer $N$, we know that there are finitely many tuples $(n,a_0,\ldots,a_n)$ that satisfy,
\[ n + \abs{a_0}+\abs{a_1} + \cdots + \abs{a_n} = N\]

Let $Q_N$ be the set of polynomials with degree $n$ and coefficient $a_0, \ldots, a_n$ such that they satisfy the above condition, i.end
\[ Q_N = \{ P \in \ZZ[x] \mid \deg(P)=n \text{ and } n + \abs{a_0}+\abs{a_1} + \cdots + \abs{a_n} = N \} \] 
Then define 
\[ A_N = \{ \text{\#all the algebraic solutions to the polynomials in }Q_N \} \]

Since $Q_N$ is finite and each polynomial has at most $n$ roots,  $A_N$ is also finite. Since $A_N$ is finite we know its countable as well.
Define
\[A=\bigcup_{i=1}^{\infty} A_i\]

Thus $A$ is the set of all algebraic numbers. Since $A$ is the union of countable sets, $A$ is also countable.

\begin{problem}
    Prove that there are real numbers which are not algebraic.
\end{problem}

\vspace{4mm}
\textit{Solution.} Immediate from above problem.

\begin{problem}
    Is the set of irrational real numbers countable?
\end{problem}

\vspace{4mm}
\textit{Solution.} If set of irrational real numbers were countable then 
\[ \RR = \QQ \cup (\RR/\QQ) \]
But we know that union of countable sets are countable, and since $\QQ$ is countable we have $\RR$ is countable which is a contradiction.

\begin{problem}
    Construct a bounded set of real numbers with exactly three limit points.
\end{problem}

\vspace{4mm}
\textit{Solution.} Let $A_0$ , $A_2$ and $A_4$ be the sets such that
\[ A_0 = \left \{ \frac{1}{n} : n \in \NN \right \} ,\quad A_2 = \left \{ 2+\frac{1}{n} : n \in \NN \right \}, \quad A_4 = \left \{ 4+\frac{1}{n} : n \in \NN \right \}\]

One can check that the only limit points of $A_0$, $A_2$ and $A_4$ are $0$, $2$ and $4$ respectively.

Thus,
\[ A = A_0 \cup A_2 \cup A_4\]
has limit points $0,2$ and $4$ and is clearly bounded within $(0,5)$.