\subsection{The Minimal Polynomial}

\subsubsection{Existence of Eigenvalue on Complex Vector Spaces}

\begin{theorem}
    Every operator on a finite-dimensional non-zero complex vector space has an eigenvalue.
\end{theorem}

\begin{proof}
    Let $V$ be a finite-dimensional non-zero complex vector space of dimension $n>0$ and $T \in \LL(V)$.
    Choose $v \in V$ such that $v \neq 0$. Then 
    \[ v, Tv, T^2v,\ldots,T^nv \]
    This has length $n+1>n$ thus it is linearly dependent list. Therefore there exists $a_0,\ldots,a_n \in \CC$ not all zero, such that
    \[ a_0v+a_1 Tv + \cdots + a_n T^nv = 0 \] 
    Let $p(z)=a_0+a_1z+\cdots+a_nz^n$ be a polynomial with minimal degree such that $p(T)=0$.
    Since $a_i \in \CC$ there exist complex roots $\lambda$ and a polynomial $q(z)$ such that
    \[ p(z)=(z-\lambda)q(z) \]
    Apply $T$ to this polynomial gives us,
    \[ p(T)=(T-\lambda)(q(T)) \]
    and applying $v$ gives us,
    \[ (T-\lambda)(q(T)v)=0 \implies T(q(T)v)=\lambda q(T)v \]
    Thus $\lambda$ is an eigenvalue as $ Tv \neq 0$ because $q(T)v \neq 0$ deu to the minimality of $p$.
\end{proof}

\begin{theorem}
    Suppose $V$ is a finite-dimensional and $T \in \LL(V)$. Then there is a unique monic polynomial $p \in \PP(\FF)$ of smallest degree
    such that $p(T)=0$. Furthermore, $\deg  p \le \dim V$.
\end{theorem}

\begin{proof}
We proceed by induction on $\dim V$. If $\dim V = 0$, then $I$ is the zero operator, and we take $p(z) = 1$, which is monic and
 has $\deg p = 0 \le 0$.

Suppose $\dim V > 0$ and the result holds for all operators on spaces of smaller dimension. Pick a non-zero vector $v \in V$. 
The list $v, Tv, \dots, T^{\dim V}v$ has length $1 + \dim V$, so it is linearly dependent. By linear dependence, lemma there exists a 
smallest positive integer $m$ such that $T^m v$ is a linear combination of $v,Tv,\ldots,T^{m-1}v$. 
Thus, there exist scalars $c_0, \dots, c_{m-1}$ such that:
\[ c_0 v + c_1 Tv + \dots + c_{m-1} T^{m-1}v + T^m v = 0 \]
Define the monic polynomial $q(z) = z^m + c_{m-1}z^{m-1} + \dots + c_0$. Then $q(T)v = 0$.

By the choice of $m$, the list $v, Tv, \dots, T^{m-1}v$ is linearly independent. Since $q(T)(T^k v) = T^k(q(T)v) = 0$, all $m$ vectors 
in this list are in $\text{null } q(T)$. Thus, $\dim \text{null } q(T) \ge m$ (by Independent list $>$ span list inequality).
By the Fundamental theorem of linear maps,
\[ \dim \text{range } q(T) = \dim V - \dim \text{null } q(T) \le \dim V - m \]
Since $\text{range } q(T)$ is invariant under $T$, we apply the induction hypothesis to $T|_{\text{range } q(T)}$. There exists a monic 
polynomial $s$ with $\deg s \le \dim V - m$ such that $s(T|_{\text{range } q(T)}) = 0$.

Let $p = sq$. Then $p$ is monic and $\deg p = \deg s + \deg q \le (\dim V - m) + m = \dim V$.
For any $v \in V$, $q(T)v \in \text{range } q(T)$, so $s(T)(q(T)v) = 0$. Thus $p(T) = 0$.
\end{proof}

Here is another way to prove the existence of minimal polynomial and its uniqueness. The proof below doesn't prove the inequality
$\dim V \ge \deg p$.  

\begin{proof}
    let $n= \dim V$ then $\dim \LL(V) = n^2$. Choose the list 
    \[ I,T,\ldots,T^{n^2} \] 
    This list is linearly dependent because $n^2 + 1> n^2$. Let $m$ be the smallest positive number such that $I,T,\ldots,T^m$ is 
    linearly dependent. By the linear dependence lemma we have,
    \[ T^m+a_{m-1}T^{m-1}+\cdots+a_0I=0 \] 
    Construct a monic polynomial $p(z)=z^m+a_{m-1}z^{m-1}+\cdots+a_0$. By the choice of $m$ this is the smallest degree monic polynomial
    which satisfies $p(T)=0$.

    For the uniqueness, suppose $p \neq q \in \PP(\FF)$ are monic polynomial such that $p(T)=0$ and $q(T)=0$. Let $h(z)=p(z)-q(z)$.
    Notice that $\deg h < m$ because both are monic and have same degree and since $p \neq q$ we have $h \not \equiv 0$.
    Thus $h(T)=p(T)-q(T)=0$ which contradicts our previous statement.
\end{proof}

\begin{definition}
    Suppose $V$ is a finite-dimensional and $T \in \LL(V)$. Then the \textit{minimal polynomial} of $T$ is the unique monic polynomial 
    $p \in \PP(\FF)$ of smallest degree such that $p(T)=0$.
\end{definition}

\begin{proposition}
    Suppose $V$ is finite-dimensional and $T \in \LL(V)$.
    \begin{enumerate}
        \item $\lambda$ is a root of the minimal polynomial $\iff$ $\lambda$ is an eigenvalues of $T$.
        \item If $V$ is a complex vector space, then minimal polynomial has the form 
            \[ (z-\lambda_1)\cdots(z-\lambda_m) \]
            where $\lambda_1,\cdots,\lambda_m$ is a list of all eigenvalues of $T$, possibly with repetition.
    \end{enumerate}
\end{proposition}

\begin{proof}
    For $(1.)$,
    Let $p$ be a minimal polynomial and suppose $\lambda$ is a root of the minimal polynomial.
    Then, we know by \textbf{FTA} we can write $p$ as $p(z) = (z-\lambda)q(z)$ for some $q(z)$. Applying this Polynomial to $T$ we get 
    \[ p(T)v=(T-\lambda I)(q(T)v)\]
    for all $v \in V$. We know that $q(T)v \neq 0$ for some $v \in V$ because $\deg q < \deg p$ and $q(T)v=k$, 
    thus $T(k)=\lambda k$. Hence $\lambda$ is an eigenvalue.

    \bigskip

    Now, let $\lambda \in \FF$ be a eigenvalue of $T$. Then, $T^k(v)=\lambda^k v$. Thus,
    \[ p(T)v = p(\lambda) v \implies p(\lambda) v = 0 \implies p(\lambda)=0\] 
    Thus $\lambda$ is a root of the polynomial.
    
    \bigskip

    For $(2.)$, Use $(1.)$ and \textbf{FTA}.
\end{proof}

\begin{proposition}
    Suppose $V$ is finite-dimensional, $T \in \LL(V)$ and $q \in \PP(\FF)$. Then $q(T)=0 \iff$ $q$ is a polynomial multiple of the minimal
    polynomial.
\end{proposition}

\begin{proof}
    Let $p$ be the minimal polynomial. Then, $\exists s,r$ such that $\deg r < \deg p$ and 
    \[ q = ps + r \]
    We have
    \[ 0 = q(T)= p(T)s(T)+r(T)=r(T) \]
    Thus $r \equiv 0$ as if not then would violets $p$ being the minimal polynomial. Thus $q=ps$.
\end{proof}

\begin{proposition}
    Suppose $V$ is a finite-dimensional, $T \in \LL(V)$, and $U$ is a subspace of $V$ that is invariant under $T$. Then the minimal
    polynomial of $T$ is a multiple of minimal polynomial of $T|_U$. 
\end{proposition}

\begin{proof}
    Let $p$ be the minimal polynomial of $T$. Then, $p(T)v=0$ for every $v \in V$. Therefore, $p(T)u = 0$ for every $u \in U$.
    Since $T$ is invariant under $U$ we have $p(T|_U) =0$. Thus using previous results we get that $p$ is a multiple of the minimal 
    polynomial of $T|_U$.
\end{proof}

\begin{proposition}
    Suppose $V$ is finite-dimensional and $T \in \LL(V)$. Then $T$ is not invertible if and only if constant term of minimal polynomial
    $p$ of $T$ is $0$. 
\end{proposition}

\begin{proof}
    \begin{align*}
        T \text{ is not invertible } &\iff  0 \text{ is an eigenvalue of }T \\
        &\iff 0 \text{ is a root of }p \\
        &\iff \text{constant term of } p \text{ is zero.}
    \end{align*}
\end{proof}